Alexis Roche

### 2020-05-06 cv/cv.tex
CV update

\noindent Senior-level engineer and applied researcher with a specialist expertise in computer vision, medical image analysis and machine learning, operating in the fields of applied research, healthcare, electro-domestic and entertainment industry. Graduated from the French ``Grande \'Ecole" CentraleSupelec (formely, Centrale Paris), and holder of a PhD. Strong experience in developing research and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, machine learning, deep learning, statistics, brain imaging, Python.

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 5754 citations, h-index: 32, i10-index: 56 (September 2019).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}

>>>>

\noindent Senior-level engineer and applied researcher with a specialist expertise in computer vision, medical image analysis and machine learning, operating in the fields of applied research, healthcare, electro-domestic and entertainment industry. Graduated from the French ``Grande \'Ecole" CentraleSupelec (formely, Centrale Paris), and holder of a PhD. Strong experience in developing research and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, machine learning, deep learning, statistics, brain imaging, Python, C.

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6102 citations, h-index: 34, i10-index: 62 (April 2020).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}
